%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}

\def\thanks#1{%
\begingroup
\leftskip1em
\noindent #1
\par
\endgroup
}

I would like to thank my team: Bratislav Svetozarevic, Moritz Begle and Stefan Caranovic. Through all the late nights, near impossible problems, and moments of genius we managed to get this technology working. I would also like to thank my students that played an important role in this thesis. In particular Nico Offeddu, Michale Jansen, Jerimias Schmidli, Maruo Luzzatto, Justin Zarb, and Stefan Caranovic (yes Stefan, you were mentioned twice...)

I would then like to thank my direct supervisors. Arno Schlueter for supervising my research throughout my PhD, Zoltan Nagy for getting me started through the complications of the first year and continuing to support as my co-supervisor till the end, and Johannes Hofer for being a mentor through the end stages of my work. 

Next on the list come the rest of the A/S Team. In particular I would like to thank Daren Thomas for his support in software development and general fun, Mario Frei for his electronics support and German language proof reading, Jimeno Fonseca for supervising me in the first weeks and introducing me to the world of building engineering, Clayton Miller for his python support, Anja Willmann for supporting with architectural aspects of the design, and Geroid Lydon for managing the HiLo development. I would also like to extend this thank you to Amr Elesawy, Illias Hischer, Martin Mosteiro Romero, Hu Zhao for their inspiration and always there for a coffee or beer break. From the Singapore team, I would like to thank Gabriel Happle and Shan-Shan Hsieh for supporting me in the development of the RC Model. I would like to also thank Niko Herren for supporting me in life cycle assessments. 

I would like to extend this thank you to the HiLo and HoNR project members for the design and construction of the ASF: Supermanoeuvre (Sydney Australia) and the Professorship of Architecture and Structures (BRG, ETH Zurich) for their work in designing the HiLo building; and the Institute of Structural Engineering (IBK, ETH Zurich) for their work in designing the HoNR building. In particular, I would like to thank Dave Pigram for leading the architectural integration of the ASF to HiLo.

Finally, I would like to thank my friends and family for always being there for me.



\endgroup
